Making multiple-locus association mapping on a genome-wide scale routine

### 2016-01-29 AM+draft.tex
2901 Changed paragraph in intro on advancements in gwa mapping methods

@@

>>>>

\section{Introduction}

@@

Over the past decade, there have also been impressive advancements in genome wide association mapping methods, the statistical techniques for measuring the strength of association between a marker locus and trait. Traditionally, association data were analysed with simple contingency tests or Cochran-armitage  trend tests. Today, far more statistically sophisticated methods are available. One such method is the  QK approach, a linear mixed model framework for genome wide association mapping (refs).  Several highly efficient 
computer programs for performing QK-based association mapping are available. Programs such as EMMA, fastLMM, GEMMA, and 
XXX(ref) make feasible the analysis of data from hundreds of thousands of snps, collected on thousands of subjects. However, not all 
areas of genome-wide association mapping have advanced. It still remains standard practice to analyse genome-wide association data 
by measuring the strength of association between a marker locus and trait for each locus separately.
